Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2020-12-28 GWLDCII.tex
changes while on the phone

This paper continues the program of establishing concrete connections between the combinatorics of the Wilson loop diagram as determined by the physics, and the combinatorics of the associated positroid cell as identified in \cite{wilsonloop}. In this paper, we give an algorithm to read the Grassmann necklace, one of the standard combinatorial characterizations of the positroid cell, directly off the Wilson loop diagram. We also show that the positroid cells associated to Wilson loop diagrams are all $3k$-dimensional, where $k$ is the number of propagators in the diagram; by contrast, the BCFW cells are all $4k$-dimensional \cite{Arkani-Hamed:2013jha}. In \cite{non-orientable} the authors note that the Wilson loop diagrams only correspond to positroid cells when the gauge vector is ignored. Including the gauge vector defines a $4k$ dimensional subspace of $\mathbb{G}r_\R(k,n+1)$.

@@

Note that the propagators in a Wilson loop diagram are undirected, that is $\cP$ defines a symmetric binary relation on $V$.  However, in some of the later arguments we need to impose a direction on a propagator $p = (i,j)$, for example in order to consider the region ``inside'' or ``outside'' of $p$. In this case, we write $(p,<_i)$ to indicate that $p$ is directed from edge $i$ to edge $j$, and $(p,<_j)$ for the opposite direction.

@@

On both of the last two points, we differ from the standard convention in the physics literature, where propagators are written as ordered pairs $(i,j)$ with $1 \leq i<j \leq n$.  Additionally, note that in this paper, we allow for the propagator set $\cP$ to be empty. This is for mathematical convenience, even though these diagrams do not correspond to tree level scattering amplitudes.
\hlfix{}{I changed the last three paragraphs a certain amount more on account of referee M's comments 3 and 4 -- we should discuss it.} \sanote{should we make a comment about propagators being multisets here (in addition to changes below)? I remember parallel edges being bad being news to Lionel when I wrote the original paper.}

@@

All three of these conditions arise from the physical interpretation of Wilson loop diagrams.  The first condition comes from the fact that these diagrams represent $N^k$MHV interctions, where $k +4 <n$, see for instance the explanation in the introduction of \cite{Adamo:2011pr}.  The second condition can be derived from the integrals associated to the diagrams, as in \cite[Theorem 1.13]{wilsonloop}. Note that the second condition prohibits propagators that connect two adjacent edges. In our definition, $\cP$ is a set so we may not have two propagators starting and ending on the same pair of edges, but we have lost nothing of physical value by not allowing multiple propagators ending on the same pair of edges since these would also fail the second condition. The third condition comes from the fact that these Wilson loop diagrams are a representation of planar Feynman diagrams of $N=4$ SYM theory. For a description of the relationship between planar Feynman diagram and planar Wilson loops, see the discussion in \cite[section 3]{LipsteinMason}.
\hlfix{}{I changed the previous 2 paragraphs quite a bit, to separate the math intuition from the physical reasoning.}  \sanote{fixed cittation issues. Like the  rewrite}

@@

  Because the nonzero entries of $C(W)$ are independent indeterminants, $J$ is an independent set if and only if there is some choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns. Each entry in $C(W)$ identifies a propagator by the row of the entry and a vertex by the column of the entry.  The entry is nonzero if and only if the propagator is supported on that vertex.  \hlfix{Consequently, take a choice of $|J|$ nonzero entries of $C(W)$, one in each row associated to an element of $J$ and each in different columns.  Each such choice is equivalent to an assignment of the propagators of $J$ to supporting vertices so that no two are assigned to the same vertex.}{Added parenthetical commas according to M.23. better?  I did a bit more, we can discuss}  Such an assignment of the propagators of $J$ to supporting vertices is exactly a map $f$ as described in the statement, hence proving the result.
\end{proof}

@@

By relating the behavior of the propagators in $W$ to the matroidal properties of $M(W)$, Agarwala and Marin-Amat also show that $M(W)$ is a positroid whenever $W$ is admissible \cite[Corollary 3.39]{wilsonloop}. \todo{check tenses throughout (M.24) -- maybe past is better, see the ``had'' at the beginning of the next paragraph, can we discuss?}

However, to go from the Wilson loop diagram $W$ to the positroid cell, one had to go through the matroid explicitly realized via $C(W)$, then make a list of all its nonzero $k\times k$ minors and extract the Le diagram or Grassmann necklace via the methods described in Section~\ref{sec:positroid background}. In \cite[section 4]{casestudy}, Agarwala and Fryer apply this process in the smallest non-trivial case: admissible Wilson loop diagrams with two propagators on six vertices. Even in this simple case, we see that the mapping from admissible Wilson loop diagrams to positroid cells is neither one-to-one nor onto, and the process described above makes it almost impossible to track the relationship between the original Wilson loop diagram and the resulting positroid.

@@

\begin{dfn}\label{props inside p}
Let $W = (\cP, [n])$ be a weakly admissible Wilson loop diagram, with $p \in \cP$ supported on edges $i$ and $j$. Write $(p, <_i)$ to represent the same propagator directed from $i$ to $j$. Then the sets of propagators {\bf inside} and {\bf outside}  $(p,<_i)$\todo{drop the 'of' throughout. Old: inside of $(p,<_i)$, New: inside $(p,<_i)$} are defined to be
\begin{gather*}\cP_{in}(p,<_i) = \{ (k,l) \in \cP \ |\ i \leq_i k <_i l \leq_i j \}, \\
\cP_{out}(p,<_i) = \cP\setminus \cP_{in}(p,<_i),
\end{gather*}
respectively.
\end{dfn}
Note that we have $p\in \cP_{in}(p, <_i)$ and so $\cP_{in}(p, <_i) = \cP_{out}(p, <_j)\cup\{p\}$.

@@

\begin{lem}\label{lem sian}
  Let $W$ be a weakly admissible Wilson loop diagram with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two conditions holds.
  \vspace{-0.5em}
  \begin{enumerate}
    \item $W$ has a propagator of length at most 6 with a propagator of length 2 on one side of it and nothing else on that side.\label{item big and 2} \todo{M.28 may need to be propagated}
    \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator has an end between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
  \end{enumerate}
See Figure~\ref{fig: small configs} for an illustration of the two configurations.
\end{lem}

@@

\begin{rmk}\todo{M.36 wants this to be a remark. I disagree? But also note that there's nothing being defined here. -- how about this?}
Given $W=(\cP, [n])$ and $i\in [n]$, the order in which the propagators contribute to the algorithm as it constructs $I_i$ defines an order on $\cP$.
  %  There is an ordering on the propagators on $W = (\cP, [n])$ defined by $I_i$. This is the ordering in which they contribute to the algorithm as it constructs $I_i$.
%  $\cP = \{p_1, \ldots p_k\}$, where 
% \[I_i = \{I_i(p_1) <_i I_i(p_2) <_i \ldots <_i I_i(p_k)\}.\]
% (The superscript $W$ is omitted here to simplify the notation.)\note{Sian tweaked this slightly to emphasise the $<_i$ order, because standard convention in most papers is to write all GN terms in the 1-order.}

@@

       m & \text{if $r =p$ and $j$ is not in the support of $p$} \\
       I_{j}^{V}(r) & \text{if $r\neq p$ and $j$ is not in the support of $p$}\; .\end{cases} 
       \]  \todo{make certain that there are periods after displays that end sentences.}
This completes the analysis of $I_j^W$. Finally, we consider what happens when we start the algorithm at vertex $j+1$. If $j+1$ is in the support of $p$ then we can argue as above to get
\[
       I_{j+1}^{W}(r)  = \begin{cases}
         j+1 & \text{if $r=p$ and $j+1$ is in the support of $p$}\\
         I_{j+2}^{V}(r) & \text{if $r\neq p$ and $j+1$ is in the support of $p$}\;.
       \end{cases}
       \]
Now suppose $j+1$ is not in the support of $p$. If we start at $j+1$ we need to know whether there are any unassigned propagators supported on edge $i$ when we reach vertex $i$. We already know that $J_q^{V}(j+1) = \{j+1\}$; in particular this means that $q$ contributes $i$ in $I_{j+2}^{V}$, by the induction hypothesis applied to $V$. However the construction of $I^{V}_{j+1}$ first assigns $q$ to $j+1$ and proceeds identically to $I^{V}_{j+2}$.  In particular if $i$ was assigned in $I^{V}_{j+1}$, then it would not be available to assign to $q$ in $I^{V}_{j+2}$ as all other propagators supported at $i$ in $V$ come before $q$.

@@

Note that the positroid cells associated to the Amplituhedron are of dimension $4|\cP|$. In \cite[section 2]{non-orientable}, Agarwala and Marcott associate a Deodhar component\footnote{Since Deodhar components play no role in this paper, the interested reader is referred to \cite{non-orientable} for more details on this.} to each Wilson loop diagram, and show that the dimension of this Deodhar component is the sum of $|\cP|$ and the dimension of the associated positroid cell.
%\[|\cP| + \text{ the dimension of associated positroid cell}.\]
Combining this with Theorem~\ref{thm dim}, we see that the Deodhar component associated to a Wilson loop diagram is $4|\cP|$-dimensional, showing that the geometry underlying the Wilson loop diagrams is consistent with the geometry underlying the Amplituhedron. It is worth noting that the Amplituhedon is defined by a projection of a set of $4|\cP|$ dimensional positroid cells, while the $4|\cP|$-dimensional cells of the Wilson loop diagram lie in $\mathbb{G}r_\R$. To  date, there is no evidence to suggest that the $3|\cP|$ dimensional positive cells of $\Gr(|\cP|, n)$ defining the Wilson loop diagrams are related to the $4|\cP|$ dimensional positive cells defining the Amplituhedron.  \sanote{This para adresses point 3 of report Y. Should there be a similar paragraph in the intro? Should it be moved?} \sanote{futzed some  more}

Marcott in \cite[Theorem 8.4]{WLDdim} also gives a proof of the $3|\cP|$-dimensionality of $M(W)$ which is much more geometric. However, it is not easy to track the effect of a particular propagator in that proof. By contrast, our approach is\todo{The transition between these paragraphs has been messed up a bit} much more constructive, and elucidates how each additional propagator contributes to tthe dimension. \sanote{fiddled with this transition} By combining Algorithms~\ref{alg:put GN on WLD} and \ref{alg:GN to Le} (converting from Wilson loop diagram to Grassmann necklace, and Grassmann necklace to Le diagram respectively) we explicitly describe the effect of adding another propagator to a Wilson loop diagram in terms of the plusses of the associated Le diagrams. Recall that the dimension of a positroid cell is equal to the number of plusses in its associated Le diagram \cite[Theorem 6.5]{Postnikov}.  Thus understanding the effect of adding another propagator is sufficient to give a recursive proof of the $3|\cP|$-dimensionality of the cells.

@@

By Corollary~\ref{no coloops} we know that $i \not\in I_1^W$, and so $i$ must label a horizontal edge on the boundary of the Le diagram of $W$, i.e. it must be a column label. The shapes of the Le diagram of $V$ and $W$ are the same except for the insertion of this column, since $I_1$ is the same for $V$ and $W$ except for the incrementation of the indices  greater than or equal to $i$ in the transition from the necklace for $V$ to the necklace for $W$.  \todo{fix mixing words and notation (M.28, M.49) throughout, esp wrt <, > $\geq$ etc.} 
\end{proof}
\vspace{0.5em}

@@

Finally, if $n-2$ and$ n-1$ are in $I_{n-2}^{V}$ then $I_{n-2}^W(q) = n-2$ and $I_{n-2}^W(p) = n-1$ as above, but some other propagator must have contributed $n-1$ to $I_{n-2}^{V}$ so we cannot use the same argument as above. \hlfix{When, in the algorithm, the construction of $I_{n-2}^W$ reaches vertex $n$,}{M.54 wants "When in the algorthm". I disagree. -- how about this compromise} only the propagators $p$ and $q$ have contributed; thus we proceed as in the construction of $I_n^{V}$ but without propagator $q$ by Remark \ref{rmk algorithm locally same}. By Lemma~\ref{vertex cyclic int lem} we know that $I_n^V(q) = n-5$, and from Remark \ref{clockwise ordering rem} we see that the only way this could occur is if $q$ was the last to contribute to $I_{n-2}^V$. %all other propagators in $V$ had already been assigned when we reached vertex $n-5$; thus $q$ was the final propagator contributing to $I_n^{V}$. 
Therefore, $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$ in this case. This completes all cases for $I_{n-2}^{W}$.

@@

\item As in Lemma~\ref{lem I} we have that none of $n,\; n-1, \; n-2$ and $n-3$ are in $I_1^V$, which implies the first part of the claim. The second part is a consequence of the discussion following equation \eqref{eq necklace}, which shows that $n-4 \not\in I_n^V$. \todo{propagate M.58 when it appears inline}

@@

 The pairing is defined as follows:
  \begin{itemize}
  \item The plusses in the $\mathcal{B}$ region of both Le diagrams are identical, so each plus in this region is paired with itself.
  \item Every square containing a plus in the leftmost two columns (the $n^{th}$ and the $(n-1)^{th}$ columns) \todo{generally turn $n$ to $n^{th}$ throughout M.60 -- I disagree and for reasons I can articulate} of $\mathcal{A}$ for $V$ also contains a plus in $W$, so these plusses are also paired with themselves.
  \item The plusses in the $n-3$ column for $V$ are paired with the corresponding plusses in the $n-2$ column for $W$.
  \item If there is a plus in the $n-2$ column of $\mathcal{A}$ in $V$ then Lemma~\ref{lem n-2 bad} applies, so there is exactly one such plus in this column. If $n-4 \not\in I_1^V$ then pair this plus with the $(n-5)\rightarrow (n-1)$ plus in $W$, whereas if $n-4 \in I_1^V$ then pair it with the $(n-5) \rightarrow n$ plus in $W$.

@@

\begin{eg}
Consider the Wilson loop diagram in Figure~\ref{fig R eg}. Assigning propagators $p$, $q$, $r$ to rows $1,2,3$ respectively, we obtain the matrix
\[
C(W) = \begin{bmatrix} a & b & 0 & 0 & 0 & c & d \\ e & f & 0 & 0 & g & h & 0 \\ i & j & 0 & k & l & 0 & 0 \end{bmatrix}.
\]
The Grassmann necklace of this diagram \hlfix{is}{M.65 wants to replace with "consists of". I disagree -- let's discuss} 
\begin{gather*}I_1 = \{1,2,4\},\ I_2 = \{2,4,5\},\ I_3 = \{4,5,6\},\ I_4=\{4,5,6\},\\ I_5=\{5,6,7\},\ I_6 = \{6,7,1\},\ I_7=\{7,1,2\}. \end{gather*}  
Figure~\ref{fig R eg} indicates which vertex is contributed to $I_i$ by each propagator, for each $i \in [1,7]$.

>>>>

This paper continues the program of establishing concrete connections between the combinatorics of the Wilson loop diagram as determined by the physics, and the combinatorics of the associated positroid cell as identified in \cite{wilsonloop}. In this paper, we give an algorithm to read the Grassmann necklace, one of the standard combinatorial characterizations of the positroid cell, directly off the Wilson loop diagram. We also show that the positroid cells associated to Wilson loop diagrams are all $3k$-dimensional, where $k$ is the number of propagators in the diagram; by contrast, the BCFW cells are all $4k$-dimensional \cite{Arkani-Hamed:2013jha}. In \cite{non-orientable} the authors note that the Wilson loop diagrams only correspond to positroid cells when the gauge vector is ignored. Including the gauge vector defines a $4k$ dimensional subspace of $\mathbb{G}_\R(k,n+1)$.

@@

Note that the propagators in a Wilson loop diagram are undirected, that is, $\cP$ defines a symmetric binary relation on $V$.  However, in some of the later arguments we need to impose a direction on a propagator $p = (i,j)$, for example in order to consider the region ``inside'' or ``outside'' of $p$. In this case, we write $(p,<_i)$ to indicate that $p$ is directed from edge $i$ to edge $j$, and $(p,<_j)$ for the opposite direction.

@@

On both of the last two points, we differ from the standard convention in the physics literature, where propagators are written as ordered pairs $(i,j)$ with $1 \leq i<j \leq n$.  Additionally, note that in this paper, we allow for the propagator set $\cP$ to be empty. This is for mathematical convenience, even though these diagrams do not correspond to tree level scattering amplitudes.  Additionally, since $\cP$ is defined to be a set of pairs, parallel propagators are already excluded from this formulation, but nothing of physical importance is lost as the admissibility restriction, Definition~\ref{admisdfn}, would have excluded them on physical grounds.

@@

All three of these conditions arise from the physical interpretation of Wilson loop diagrams.  The first condition comes from the fact that these diagrams represent $N^k$MHV interctions, where $k +4 <n$, see for instance the explanation in the introduction of \cite{Adamo:2011pr}.  The second condition can be derived from the integrals associated to the diagrams, as in \cite[Theorem 1.13]{wilsonloop}. Note that the second condition prohibits propagators that connect two adjacent edges. In our definition, $\cP$ is a set so we may not have two propagators starting and ending on the same pair of edges, but we have lost nothing of physical value by not allowing multiple propagators ending on the same pair of edges since these would also fail the second condition. The third condition comes from the fact that these Wilson loop diagrams are a representation of planar Feynman diagrams of $N=4$ SYM theory. For a description of the relationship between planar Feynman diagram and planar Wilson loops, see the discussion in \cite[section 3]{LipsteinMason}.

@@

  Because the nonzero entries of $C(W)$ are independent indeterminants, $J$ is an independent set if and only if there is some choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns. Each entry in $C(W)$ identifies a propagator by the row of the entry and a vertex by the column of the entry.  The entry is nonzero if and only if the propagator is supported on that vertex.  Consequently, take a choice of $|J|$ nonzero entries of $C(W)$, one in each row associated to an element of $J$ and each in different columns.  Such a choice is equivalent to an assignment of the propagators of $J$ to supporting vertices so that no two are assigned to the same vertex.  Such an assignment of the propagators of $J$ to supporting vertices is exactly a map $f$ as described in the statement, hence proving the result.
\end{proof}

@@

By relating the behavior of the propagators in $W$ to the matroidal properties of $M(W)$, Agarwala and Marin-Amat also showed that $M(W)$ is a positroid whenever $W$ is admissible \cite[Corollary 3.39]{wilsonloop}. \todo{Decision -- make them past ------ check tenses throughout (M.24) -- maybe past is better, see the ``had'' at the beginning of the next paragraph, can we discuss?}

However, to go from the Wilson loop diagram $W$ to the positroid cell, one had to go through the matroid explicitly realized via $C(W)$, then make a list of all its nonzero $k\times k$ minors and extract the Le diagram or Grassmann necklace via the methods described in Section~\ref{sec:positroid background}. In \cite[section 4]{casestudy}, Agarwala and Fryer applied this process in the smallest non-trivial case: admissible Wilson loop diagrams with two propagators on six vertices. Even in this simple case, we see that the mapping from admissible Wilson loop diagrams to positroid cells is neither one-to-one nor onto, and the process described above makes it almost impossible to track the relationship between the original Wilson loop diagram and the resulting positroid.

@@

\begin{dfn}\label{props inside p}
Let $W = (\cP, [n])$ be a weakly admissible Wilson loop diagram, with $p \in \cP$ supported on edges $i$ and $j$. Write $(p, <_i)$ to represent the same propagator directed from $i$ to $j$. Then the sets of propagators {\bf inside} and {\bf outside}  $(p,<_i)$ are defined to be
\begin{gather*}\cP_{in}(p,<_i) = \{ (k,l) \in \cP \ |\ i \leq_i k <_i l \leq_i j \}, \\
\cP_{out}(p,<_i) = \cP\setminus \cP_{in}(p,<_i),
\end{gather*}
respectively.
\end{dfn}
Note that we have $p\in \cP_{in}(p, <_i)$ and so $\cP_{in}(p, <_i) = \cP_{out}(p, <_j)\cup\{p\}$.

@@

\begin{lem}\label{lem sian}
  Let $W$ be a weakly admissible Wilson loop diagram with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two conditions holds.
  \vspace{-0.5em}
  \begin{enumerate}
    \item $W$ has a propagator of length at most 6 with a propagator of length 2 on one side of it and nothing else on that side.\label{item big and 2}
    \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator has an end between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
  \end{enumerate}
See Figure~\ref{fig: small configs} for an illustration of the two configurations.
\end{lem}

@@

\begin{rmk}
Given $W=(\cP, [n])$ and $i\in [n]$, the order in which the propagators contribute to the algorithm during the construction of $I_i$ defines an order on $\cP$.
  %  There is an ordering on the propagators on $W = (\cP, [n])$ defined by $I_i$. This is the ordering in which they contribute to the algorithm as it constructs $I_i$.
%  $\cP = \{p_1, \ldots p_k\}$, where 
% \[I_i = \{I_i(p_1) <_i I_i(p_2) <_i \ldots <_i I_i(p_k)\}.\]
% (The superscript $W$ is omitted here to simplify the notation.)\note{Sian tweaked this slightly to emphasise the $<_i$ order, because standard convention in most papers is to write all GN terms in the 1-order.}

@@

       m & \text{if $r =p$ and $j$ is not in the support of $p$} \\
       I_{j}^{V}(r) & \text{if $r\neq p$ and $j$ is not in the support of $p$}\; .\end{cases} 
       \]  
This completes the analysis of $I_j^W$. Finally, we consider what happens when we start the algorithm at vertex $j+1$. If $j+1$ is in the support of $p$ then we can argue as above to get
\[
       I_{j+1}^{W}(r)  = \begin{cases}
         j+1 & \text{if $r=p$ and $j+1$ is in the support of $p$}\\
         I_{j+2}^{V}(r) & \text{if $r\neq p$ and $j+1$ is in the support of $p$}\;.
       \end{cases}
       \]
Now suppose $j+1$ is not in the support of $p$. If we start at $j+1$ we need to know whether there are any unassigned propagators supported on edge $i$ when we reach vertex $i$. We already know that $J_q^{V}(j+1) = \{j+1\}$; in particular this means that $q$ contributes $i$ in $I_{j+2}^{V}$, by the induction hypothesis applied to $V$. However the construction of $I^{V}_{j+1}$ first assigns $q$ to $j+1$ and proceeds identically to $I^{V}_{j+2}$.  In particular if $i$ was assigned in $I^{V}_{j+1}$, then it would not be available to assign to $q$ in $I^{V}_{j+2}$ as all other propagators supported at $i$ in $V$ come before $q$.

@@

Note that the positroid cells associated to the Amplituhedron are of dimension $4|\cP|$. In \cite[section 2]{non-orientable}, Agarwala and Marcott associate a Deodhar component\footnote{Since Deodhar components play no role in this paper, the interested reader is referred to \cite{non-orientable} for more details on this.} to each Wilson loop diagram, and show that the dimension of this Deodhar component is the sum of $|\cP|$ and the dimension of the associated positroid cell.
%\[|\cP| + \text{ the dimension of associated positroid cell}.\]
Combining this with Theorem~\ref{thm dim}, we see that the Deodhar component associated to a Wilson loop diagram is $4|\cP|$-dimensional, showing that the geometry underlying the Wilson loop diagrams is consistent with the geometry underlying the Amplituhedron. It is worth noting that the Amplituhedon is defined by a projection of a set of $4|\cP|$ dimensional positroid cells, while the $4|\cP|$-dimensional cells of the Wilson loop diagram lie in $\mathbb{G}_\R$.
While it is conjectured that the geometry of the Amplituhedron is related to the geometry of the Wilson loop diagrams, in part due to their common physical origin, the $3 |\cP|$ dimensional positroid cells defined by the Wilson loop diagrams do not seem to bear any geometric relationship to the $4|\cP|$ dimensional cells parametrized by the Amplituhedron.
%To  date, there is no evidence to suggest that the $3|\cP|$ dimensional positive cells of $\Gr(|\cP|, n)$ defining the Wilson loop diagrams are related to the $4|\cP|$ dimensional positive cells defining the Amplituhedron.  \sanote{This para adresses point 3 of report Y. Should there be a similar paragraph in the intro? Should it be moved?} \sanote{futzed some  more}

Marcott in \cite[Theorem 8.4]{WLDdim} also gives a proof of the $3|\cP|$-dimensionality of $M(W)$ which is much more geometric. However, it is not easy to track the effect of a particular propagator in that proof. By contrast, our approach is much more constructive, and elucidates how each additional propagator contributes to tthe dimension. By combining Algorithms~\ref{alg:put GN on WLD} and \ref{alg:GN to Le} (converting from Wilson loop diagram to Grassmann necklace, and Grassmann necklace to Le diagram respectively) we explicitly describe the effect of adding another propagator to a Wilson loop diagram in terms of the plusses of the associated Le diagrams. Recall that the dimension of a positroid cell is equal to the number of plusses in its associated Le diagram \cite[Theorem 6.5]{Postnikov}.  Thus understanding the effect of adding another propagator is sufficient to give a recursive proof of the $3|\cP|$-dimensionality of the cells.

@@

By Corollary~\ref{no coloops} we know that $i \not\in I_1^W$, and so $i$ must label a horizontal edge on the boundary of the Le diagram of $W$, i.e. it must be a column label. The shapes of the Le diagram of $V$ and $W$ are the same except for the insertion of this column, since $I_1$ is the same for $V$ and $W$ except for the incrementation of the indices  greater than or equal to $i$ in the transition from the necklace for $V$ to the necklace for $W$. 
\end{proof}
\vspace{0.5em}

@@

Finally, if $n-2$ and$ n-1$ are in $I_{n-2}^{V}$ then $I_{n-2}^W(q) = n-2$ and $I_{n-2}^W(p) = n-1$ as above, but some other propagator must have contributed $n-1$ to $I_{n-2}^{V}$ so we cannot use the same argument as above.  When, in the algorithm, the construction of $I_{n-2}^W$ reaches vertex $n$, only the propagators $p$ and $q$ have contributed; thus we proceed as in the construction of $I_n^{V}$ but without propagator $q$ by Remark \ref{rmk algorithm locally same}. By Lemma~\ref{vertex cyclic int lem} we know that $I_n^V(q) = n-5$, and from Remark \ref{clockwise ordering rem} we see that the only way this could occur is if $q$ was the last to contribute to $I_{n-2}^V$. %all other propagators in $V$ had already been assigned when we reached vertex $n-5$; thus $q$ was the final propagator contributing to $I_n^{V}$. 
Therefore, $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$ in this case. This completes all cases for $I_{n-2}^{W}$.

@@

\item As in Lemma~\ref{lem I} we have that none of $n,\; n-1, \; n-2$ and $n-3$ are in $I_1^V$, which implies the first part of the claim. The second part is a consequence of the discussion following equation \eqref{eq necklace}, which shows that $n-4 \not\in I_n^V$.

@@

 The pairing is defined as follows:
  \begin{itemize}
  \item The plusses in the $\mathcal{B}$ region of both Le diagrams are identical, so each plus in this region is paired with itself.
  \item Every square containing a plus in the leftmost two columns (the $n^{th}$ and the $(n-1)^{th}$ columns) \todo{Put note in paper and response to referee --- generally turn $n$ to $n^{th}$ throughout M.60 -- I disagree and for reasons I can articulate} of $\mathcal{A}$ for $V$ also contains a plus in $W$, so these plusses are also paired with themselves.
  \item The plusses in the $n-3$ column for $V$ are paired with the corresponding plusses in the $n-2$ column for $W$.
  \item If there is a plus in the $n-2$ column of $\mathcal{A}$ in $V$ then Lemma~\ref{lem n-2 bad} applies, so there is exactly one such plus in this column. If $n-4 \not\in I_1^V$ then pair this plus with the $(n-5)\rightarrow (n-1)$ plus in $W$, whereas if $n-4 \in I_1^V$ then pair it with the $(n-5) \rightarrow n$ plus in $W$.

@@

\begin{eg}
Consider the Wilson loop diagram in Figure~\ref{fig R eg}. Assigning propagators $p$, $q$, $r$ to rows $1,2,3$ respectively, we obtain the matrix
\[
C(W) = \begin{bmatrix} a & b & 0 & 0 & 0 & c & d \\ e & f & 0 & 0 & g & h & 0 \\ i & j & 0 & k & l & 0 & 0 \end{bmatrix}.
\]
The Grassmann necklace of this diagram is
\begin{gather*}(I_1 = \{1,2,4\},\ I_2 = \{2,4,5\},\ I_3 = \{4,5,6\},\ I_4=\{4,5,6\},\\ I_5=\{5,6,7\},\ I_6 = \{6,7,1\},\ I_7=\{7,1,2\}). \end{gather*}  
Figure~\ref{fig R eg} indicates which vertex is contributed to $I_i$ by each propagator, for each $i \in [1,7]$.
